**Bayesian statistics for longitudinal studies in biomedical research**

### 2020-12-31 Manuscripts/Manuscript_AM_v1.Rmd
updated manuscript and references

In GAMs the smooth functions are represented using _basis functions_ function over  evenly spaced ranges of the covariates known as _knots_. In particular, the _basis function_ used is a cubic spline, which is a smooth curve constructed from cubic polynomials joined together[@wood2017;@simpson2018].

>>>>

In GAMs the smooth functions are represented using _basis functions_  over  evenly spaced ranges of the covariates known as _knots_. The _basis function_ used is a cubic spline, which is a smooth curve constructed from cubic polynomials joined together[@wood2017;@simpson2018]. Cubic splines have a long history in their use to solve non-parametric statistical problems and are the default choice to fit GAMs as they are the simplest option to obtain visual smoothness [@wegman1983].
